---
title: "Belonging in STEM survey tidysesh"
author: "JP Flores"
date: "5/3/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load the packages 
```{r}
library(tidyverse)
library(readxl)
library(janitor)
library(plotly)
```

Import the data
```{r}
bestem_data <-read_csv("/Users/jpflores/Desktop/Desktop - JP’s MacBook Pro/bestem/data through 5_30.xlsx - anonymizing the data.csv")

# View(bestem_data)

bestem_data <- bestem_data %>% 
  select(- `Row # from Qualtrics`,
         - ResponseId,- X15, - X16, - X17, - X27, - X28, - X29, - X39, - X40,
         - X41, - X51, - X52, - X53, - X63, - X64, - X65, - X75, - X76, - X77, - X87, - X88, - X89,
         - X99, - X100, - X101, - X111, - X112, - X113, - X123, - X124, - X125, - X135, - X136,
         - X137, - X147, - X148, - X149, - X159, - X160, - X161, - X171, - X172, - X173, - X183,
         - X184, - X185, - X195, - X196, - X197, - X207, - X208, - X209, - X219, - X220,
         - X221, - X231, - X232, - X233, - X243, - X244, - X245, - X255, - X256, - X257,- X267,
         - X268, - X269, - X279, - X280, - X281, - X291, - X292, - X293, - X303, -X304, - X305,
         - X315, - X316, - X317, - X327, - X328, - X329, - X339, - X340, - X341, - X351, - X352,
         - X353, - X363, - X364, - X365, - X375, - X376, - X377, - X387, - X388, - X389, - X399,
         - X400, - X401, - X411, - X412, - X413, - X423, - X424, - X438, - X440, - X441, - X442, - X443, 
         - X444, - X445, - X447, - X448
         )

bestem_data <- bestem_data[-c(1:2) , ]

bestem_data <- bestem_data %>% 
  mutate(comfort_peers_classes_1 = comfort_peers_classe_1)

# bestem_data %>%
#   count(major)
```


Add column (Were they a declared STEM major? ex. Biochemistry, Biology, Chemistry, Computer Science, Cognitive Science, Geology, Kinesiology, Mathematics, Physics, or Psychology)
```{r}
declared_stem <- bestem_data %>% 
  filter(any_STEM == "Yes") %>% 
  filter(know_major == "Yes") %>% 
  filter(major %in% c("Biology", "Biochemistry", "Chemistry", "Computer Science", "Cognitive   Science","Geology","Kinesiology", "Mathematics", "Physics", "Psychology", "Computer Science,Economics", "Cognitive Science,Philosophy", "Cognitive Science,Group Language", "Biology,Kinesiology,Psychology", "Computer Science,Economics", "Art & Art History,Biology",
"Biochemistry,Biology", "Biochemistry,Computer Science", "Biochemistry,Theater",
"Biology,Theater", "Biology,Cognitive Science", "Chemistry,Chinese Studies", "Cognitive Science,Computer Science", "Cognitive Science,Economics", "Cognitive Science,Theater", "Comparative Studies in Literature and Culture,Computer Science", "Comparative Studies in Literature and Culture,Mathematics", "Computer Science,Mathematics", "Computer Science,Media Arts & Culture",
"Computer Science,Physics", "Computer Science,Theater", "Economics,Mathematics", "Mathematics,Physics", "Psychology,Spanish Studies"))

         
bestem_data <- bestem_data %>%
  mutate(stem_major = case_when(
    major == "Biology" ~ "yes", 
    major == "Biochemistry" ~ "yes",
    major == "Chemistry" ~ "yes",
    major == "Computer Science" ~ "yes",
    major == "Cognitive Science" ~ "yes",
    major == "Geology" ~ "yes",
    major == "Kinesiology" ~ "yes",
    major == "Mathematics" ~ "yes",
    major == "Physics" ~ "yes",
    major == "Psychology" ~ "yes",
    major == "Art & Art History,Biology" ~ "yes",
    major == "Biochemistry,Biology" ~ "yes",
    major == "Biochemistry,Comparative Studies in Literature and Culture" ~ "yes",
    major == "Biochemistry,Computer Science" ~ "yes",
    major == "Biochemistry,Theater" ~ "yes",
    major == "Biology,Kinesiology,Psychology" ~ "yes",
    major == "Biology,Theater" ~ "yes",
    major == "Biology,Cognitive Science" ~ "yes",
    major == "Computer Science,Economics" ~ "yes",
    major == "Cognitive Science,Philosophy" ~ "yes",
    major == "Cognitive Science,Group Language" ~ "yes",
    major == "Chemistry,Chinese Studies" ~ "yes",
    major == "Cognitive Science,Computer Science" ~ "yes",
    major == "Cognitive Science,Economics" ~ "yes",
    major == "Cognitive Science,Theater" ~ "yes",
    major == "Comparative Studies in Literature and Culture,Computer Science" ~ "yes",
    major == "Comparative Studies in Literature and Culture,Mathematics" ~ "yes",
    major == "Computer Science,Mathematics" ~ "yes",
    major == "Computer Science,Media Arts & Culture" ~ "yes",
    major == "Computer Science,Physics" ~ "yes",
    major == "Computer Science,Theater" ~ "yes",
    major == "Economics,Mathematics" ~ "yes",
    major == "Mathematics,Physics" ~ "yes",
    major == "Psychology,Spanish Studies" ~ "yes",
    TRUE ~ "no"))
    # TRUE ~ NA_character_))
```

Add column (Were they an intended STEM major?)
```{r}
bestem_data <- bestem_data %>%
  mutate(intention_in_stem = case_when(
  know_major == "Not sure of the exact major, but something in STEM" ~ "yes",
  know_major == "Not sure of the major, definitely not STEM" ~ "none",
  know_major == "Not sure of the major, might be in STEM" ~ "undecided",
  know_major == "Yes" ~ "declared",
  know_major == "No, but I've already figured out my intended major(s)" ~ "No, but figured out major",
  TRUE ~ NA_character_))
```

Add column (double STEM major)
```{r}
bestem_data <- bestem_data %>% 
  mutate(double_stem = case_when(
    major == "Biochemistry,Biology" ~ "yes",
    major == "Biochemistry,Computer Science" ~ "yes",
    major == "Biology,Kinesiology,Psychology" ~ "yes",
    major == "Biology,Cognitive Science" ~ "yes",
    major == "Cognitive Science,Computer Science" ~ "yes",
    major == "Computer Science,Mathematics" ~ "yes",
    major == "Computer Science,Physics" ~ "yes",
    major == "Mathematics,Physics" ~ "yes",
    TRUE ~ "no"))
```

Add column (double non-STEM major)
```{r}
bestem_data <- bestem_data %>% 
  mutate(double_non_stem = case_when(
    major == "Art & Art History,Biology" ~ "yes",
    major == "Biochemistry,Comparative Studies in Literature and Culture" ~ "yes",
    major == "Biochemistry,Theater" ~ "yes",
    major == "Biology,Theater" ~ "yes",
    major == "Computer Science,Economics" ~ "yes",
    major == "Cognitive Science,Philosophy" ~ "yes",
    major == "Cognitive Science,Group Language" ~ "yes",
    major == "Chemistry,Chinese Studies" ~ "yes",
    major == "Cognitive Science,Economics" ~ "yes",
    major == "Cognitive Science,Theater" ~ "yes",
    major == "Comparative Studies in Literature and Culture,Computer Science" ~ "yes",
    major == "Comparative Studies in Literature and Culture,Mathematics" ~ "yes",
    major == "Computer Science,Media Arts & Culture" ~ "yes",
    major == "Computer Science,Theater" ~ "yes",
    major == "Economics,Mathematics" ~ "yes",
    major == "Psychology,Spanish Studies" ~ "yes",
    TRUE ~ "no"))
```

"Belongingness in STEM" metric (Average the responses to all questions by individual by first major)
```{r}

bestem_data$`1_fit major_1` <- as.numeric(bestem_data$`1_fit major_1`)
bestem_data$`1_welcome major_1` <- as.numeric(bestem_data$`1_welcome major_1`)
bestem_data$`1_comfort major_1` <- as.numeric(bestem_data$`1_comfort major_1`)
bestem_data$`1_thrilled major_1` <- as.numeric(bestem_data$`1_thrilled major_1`)
bestem_data$`1_like peers_1` <-  as.numeric(bestem_data$`1_like peers_1`)
bestem_data$`1_comfort peers_1` <- as.numeric(bestem_data$`1_comfort peers_1`)
bestem_data$`1_like profs_1` <-  as.numeric(bestem_data$`1_like profs_1`)
bestem_data$`1_comfort profs_1` <-  as.numeric(bestem_data$`1_comfort profs_1`)


bestem_data <- bestem_data %>% 
  rowwise() %>%
  mutate(belongingness_bio = mean(c_across(4:11)))

bestem_data$`2_fit major_1` <- as.numeric(bestem_data$`2_fit major_1`)
bestem_data$`2_welcome major_1` <- as.numeric(bestem_data$`2_welcome major_1`)
bestem_data$`2_comfort major_1` <- as.numeric(bestem_data$`2_comfort major_1`)
bestem_data$`2_thrilled major_1` <- as.numeric(bestem_data$`2_thrilled major_1`)
bestem_data$`2_like peers_1` <-  as.numeric(bestem_data$`2_like peers_1`)
bestem_data$`2_comfort peers_1` <- as.numeric(bestem_data$`2_comfort peers_1`)
bestem_data$`2_like profs_1` <-  as.numeric(bestem_data$`2_like profs_1`)
bestem_data$`2_comfort profs_1` <-  as.numeric(bestem_data$`2_comfort profs_1`)

bestem_data <- bestem_data %>% 
  rowwise() %>%
  mutate(belongingness_biochem = mean(c_across(13:20)))

bestem_data$`3_fit major_1` <- as.numeric(bestem_data$`3_fit major_1`)
bestem_data$`3_welcome major_1` <- as.numeric(bestem_data$`3_welcome major_1`)
bestem_data$`3_comfort major_1` <- as.numeric(bestem_data$`3_comfort major_1`)
bestem_data$`3_thrilled major_1` <- as.numeric(bestem_data$`3_thrilled major_1`)
bestem_data$`3_like peers_1` <-  as.numeric(bestem_data$`3_like peers_1`)
bestem_data$`3_comfort peers_1` <- as.numeric(bestem_data$`3_comfort peers_1`)
bestem_data$`3_like profs_1` <-  as.numeric(bestem_data$`3_like profs_1`)
bestem_data$`3_comfort profs_1` <-  as.numeric(bestem_data$`3_comfort profs_1`)

bestem_data <- bestem_data %>% 
  rowwise() %>%
  mutate(belongingness_chem = mean(c_across(22:29)))

bestem_data$`4_fit major_1` <- as.numeric(bestem_data$`4_fit major_1`)
bestem_data$`4_welcome major_1` <- as.numeric(bestem_data$`4_welcome major_1`)
bestem_data$`4_comfort major_1` <- as.numeric(bestem_data$`4_comfort major_1`)
bestem_data$`4_thrilled major_1` <- as.numeric(bestem_data$`4_thrilled major_1`)
bestem_data$`4_like peers_1` <-  as.numeric(bestem_data$`4_like peers_1`)
bestem_data$`4_comfort peers_1` <- as.numeric(bestem_data$`4_comfort peers_1`)
bestem_data$`4_like profs_1` <-  as.numeric(bestem_data$`4_like profs_1`)
bestem_data$`4_comfort profs_1` <-  as.numeric(bestem_data$`4_comfort profs_1`)

bestem_data <- bestem_data %>% 
  rowwise() %>%
  mutate(belongingness_cogsci = mean(c_across(31:38)))

bestem_data$`5_fit major_1` <- as.numeric(bestem_data$`5_fit major_1`)
bestem_data$`5_welcome major_1` <- as.numeric(bestem_data$`5_welcome major_1`)
bestem_data$`5_comfort major_1` <- as.numeric(bestem_data$`5_comfort major_1`)
bestem_data$`5_thrilled major_1` <- as.numeric(bestem_data$`5_thrilled major_1`)
bestem_data$`5_like peers_1` <-  as.numeric(bestem_data$`5_like peers_1`)
bestem_data$`5_comfort peers_1` <- as.numeric(bestem_data$`5_comfort peers_1`)
bestem_data$`5_like profs_1` <-  as.numeric(bestem_data$`5_like profs_1`)
bestem_data$`5_comfort profs_1` <-  as.numeric(bestem_data$`5_comfort profs_1`)

bestem_data <- bestem_data %>% 
  rowwise() %>%
  mutate(belongingness_compsci = mean(c_across(40:47)))

bestem_data$`6_fit major_1` <- as.numeric(bestem_data$`6_fit major_1`)
bestem_data$`6_welcome major_1` <- as.numeric(bestem_data$`6_welcome major_1`)
bestem_data$`6_comfort major_1` <- as.numeric(bestem_data$`6_comfort major_1`)
bestem_data$`6_thrilled major_1` <- as.numeric(bestem_data$`6_thrilled major_1`)
bestem_data$`6_like peers_1` <-  as.numeric(bestem_data$`6_like peers_1`)
bestem_data$`6_comfort peers_1` <- as.numeric(bestem_data$`6_comfort peers_1`)
bestem_data$`6_like profs_1` <-  as.numeric(bestem_data$`6_like profs_1`)
bestem_data$`6_comfort profs_1` <-  as.numeric(bestem_data$`6_comfort profs_1`)

bestem_data <- bestem_data %>% 
  rowwise() %>%
  mutate(belongingness_geo = mean(c_across(49:56)))

bestem_data$`7_fit major_1` <- as.numeric(bestem_data$`7_fit major_1`)
bestem_data$`7_welcome major_1` <- as.numeric(bestem_data$`7_welcome major_1`)
bestem_data$`7_comfort major_1` <- as.numeric(bestem_data$`7_comfort major_1`)
bestem_data$`7_thrilled major_1` <- as.numeric(bestem_data$`7_thrilled major_1`)
bestem_data$`7_like peers_1` <-  as.numeric(bestem_data$`7_like peers_1`)
bestem_data$`7_comfort peers_1` <- as.numeric(bestem_data$`7_comfort peers_1`)
bestem_data$`7_like profs_1` <-  as.numeric(bestem_data$`7_like profs_1`)
bestem_data$`7_comfort profs_1` <-  as.numeric(bestem_data$`7_comfort profs_1`)

bestem_data <- bestem_data %>% 
  rowwise() %>%
  mutate(belongingness_kines = mean(c_across(58:65)))

bestem_data$`8_fit major_1` <- as.numeric(bestem_data$`8_fit major_1`)
bestem_data$`8_welcome major_1` <- as.numeric(bestem_data$`8_welcome major_1`)
bestem_data$`8_comfort major_1` <- as.numeric(bestem_data$`8_comfort major_1`)
bestem_data$`8_thrilled major_1` <- as.numeric(bestem_data$`8_thrilled major_1`)
bestem_data$`8_like peers_1` <-  as.numeric(bestem_data$`8_like peers_1`)
bestem_data$`8_comfort peers_1` <- as.numeric(bestem_data$`8_comfort peers_1`)
bestem_data$`8_like profs_1` <-  as.numeric(bestem_data$`8_like profs_1`)
bestem_data$`8_comfort profs_1` <-  as.numeric(bestem_data$`8_comfort profs_1`)

bestem_data <- bestem_data %>% 
  rowwise() %>%
  mutate(belongingness_math = mean(c_across(67:74)))

bestem_data$`9_fit major_1` <- as.numeric(bestem_data$`9_fit major_1`)
bestem_data$`9_welcome major_1` <- as.numeric(bestem_data$`9_welcome major_1`)
bestem_data$`9_comfort major_1` <- as.numeric(bestem_data$`9_comfort major_1`)
bestem_data$`9_thrilled major_1` <- as.numeric(bestem_data$`9_thrilled major_1`)
bestem_data$`9_like peers_1` <-  as.numeric(bestem_data$`9_like peers_1`)
bestem_data$`9_comfort peers_1` <- as.numeric(bestem_data$`9_comfort peers_1`)
bestem_data$`9_like profs_1` <-  as.numeric(bestem_data$`9_like profs_1`)
bestem_data$`9_comfort profs_1` <-  as.numeric(bestem_data$`9_comfort profs_1`)

bestem_data <- bestem_data %>% 
  rowwise() %>%
  mutate(belongingness_physics = mean(c_across(76:83)))

bestem_data$`10_fit major_1` <- as.numeric(bestem_data$`10_fit major_1`)
bestem_data$`10_welcome major_1` <- as.numeric(bestem_data$`10_welcome major_1`)
bestem_data$`10_comfort major_1` <- as.numeric(bestem_data$`10_comfort major_1`)
bestem_data$`10_thrilled major_1` <- as.numeric(bestem_data$`10_thrilled major_1`)
bestem_data$`10_like peers_1` <-  as.numeric(bestem_data$`10_like peers_1`)
bestem_data$`10_comfort peers_1` <- as.numeric(bestem_data$`10_comfort peers_1`)
bestem_data$`10_like profs_1` <-  as.numeric(bestem_data$`10_like profs_1`)
bestem_data$`10_comfort profs_1` <-  as.numeric(bestem_data$`10_comfort profs_1`)

bestem_data <- bestem_data %>% 
  rowwise() %>%
  mutate(belongingness_psych = mean(c_across(85:92)))

# No data for this section
# bestem_data$`11_fit major_1` <- as.numeric(bestem_data$`11_fit major_1`)
# bestem_data$`11_welcome major_1` <- as.numeric(bestem_data$`11_welcome major_1`)
# bestem_data$`11_comfort major_1` <- as.numeric(bestem_data$`11_comfort major_1`)
# bestem_data$`11_thrilled major_1` <- as.numeric(bestem_data$`11_thrilled major_1`)
# bestem_data$`11_like peers_1` <-  as.numeric(bestem_data$`11_like peers_1`)
# bestem_data$`11_comfort peers_1` <- as.numeric(bestem_data$`11_comfort peers_1`)
# bestem_data$`11_like profs_1` <-  as.numeric(bestem_data$`11_like profs_1`)
# bestem_data$`11_comfort profs_1` <-  as.numeric(bestem_data$`11_comfort profs_1`)
# 
# bestem_data <- bestem_data %>% 
#   rowwise() %>%
#   mutate(belongingness_ = mean(c_across(94:101)))

bestem_data$`12_fit major_1` <- as.numeric(bestem_data$`12_fit major_1`)
bestem_data$`12_welcome major_1` <- as.numeric(bestem_data$`12_welcome major_1`)
bestem_data$`12_comfort major_1` <- as.numeric(bestem_data$`12_comfort major_1`)
bestem_data$`12_thrilled major_1` <- as.numeric(bestem_data$`12_thrilled major_1`)
bestem_data$`12_like peers_1` <-  as.numeric(bestem_data$`12_like peers_1`)
bestem_data$`12_comfort peers_1` <- as.numeric(bestem_data$`12_comfort peers_1`)
bestem_data$`12_like profs_1` <-  as.numeric(bestem_data$`12_like profs_1`)
bestem_data$`12_comfort profs_1` <-  as.numeric(bestem_data$`12_comfort profs_1`)

bestem_data <- bestem_data %>% 
  rowwise() %>%
  mutate(belongingness_art_arthist = mean(c_across(103:110)))

bestem_data$`13_fit major_1` <- as.numeric(bestem_data$`13_fit major_1`)
bestem_data$`13_welcome major_1` <- as.numeric(bestem_data$`13_welcome major_1`)
bestem_data$`13_comfort major_1` <- as.numeric(bestem_data$`13_comfort major_1`)
bestem_data$`13_thrilled major_1` <- as.numeric(bestem_data$`13_thrilled major_1`)
bestem_data$`13_like peers_1` <-  as.numeric(bestem_data$`13_like peers_1`)
bestem_data$`13_comfort peers_1` <- as.numeric(bestem_data$`13_comfort peers_1`)
bestem_data$`13_like profs_1` <-  as.numeric(bestem_data$`13_like profs_1`)
bestem_data$`13_comfort profs_1` <-  as.numeric(bestem_data$`13_comfort profs_1`)

bestem_data <- bestem_data %>% 
  rowwise() %>%
  mutate(belongingness_black_studies = mean(c_across(112:119)))

bestem_data$`14_fit major_1` <- as.numeric(bestem_data$`14_fit major_1`)
bestem_data$`14_welcome major_1` <- as.numeric(bestem_data$`14_welcome major_1`)
bestem_data$`14_comfort major_1` <- as.numeric(bestem_data$`14_comfort major_1`)
bestem_data$`14_thrilled major_1` <- as.numeric(bestem_data$`14_thrilled major_1`)
bestem_data$`14_like peers_1` <-  as.numeric(bestem_data$`14_like peers_1`)
bestem_data$`14_comfort peers_1` <- as.numeric(bestem_data$`14_comfort peers_1`)
bestem_data$`14_like profs_1` <-  as.numeric(bestem_data$`14_like profs_1`)
bestem_data$`14_comfort profs_1` <-  as.numeric(bestem_data$`14_comfort profs_1`)

bestem_data <- bestem_data %>% 
  rowwise() %>%
  mutate(belongingness_chinese_studies = mean(c_across(121:128)))

bestem_data$`15_fit major_1` <- as.numeric(bestem_data$`15_fit major_1`)
bestem_data$`15_welcome major_1` <- as.numeric(bestem_data$`15_welcome major_1`)
bestem_data$`15_comfort major_1` <- as.numeric(bestem_data$`15_comfort major_1`)
bestem_data$`15_thrilled major_1` <- as.numeric(bestem_data$`15_thrilled major_1`)
bestem_data$`15_like peers_1` <-  as.numeric(bestem_data$`15_like peers_1`)
bestem_data$`15_comfort peers_1` <- as.numeric(bestem_data$`15_comfort peers_1`)
bestem_data$`15_like profs_1` <-  as.numeric(bestem_data$`15_like profs_1`)
bestem_data$`15_comfort profs_1` <-  as.numeric(bestem_data$`15_comfort profs_1`)

bestem_data <- bestem_data %>% 
  rowwise() %>%
  mutate(belongingness_ctsj = mean(c_across(130:137)))

bestem_data$`16_fit major_1` <- as.numeric(bestem_data$`16_fit major_1`)
bestem_data$`16_welcome major_1` <- as.numeric(bestem_data$`16_welcome major_1`)
bestem_data$`16_comfort major_1` <- as.numeric(bestem_data$`16_comfort major_1`)
bestem_data$`16_thrilled major_1` <- as.numeric(bestem_data$`16_thrilled major_1`)
bestem_data$`16_like peers_1` <-  as.numeric(bestem_data$`16_like peers_1`)
bestem_data$`16_comfort peers_1` <- as.numeric(bestem_data$`16_comfort peers_1`)
bestem_data$`16_like profs_1` <-  as.numeric(bestem_data$`16_like profs_1`)
bestem_data$`16_comfort profs_1` <-  as.numeric(bestem_data$`16_comfort profs_1`)

bestem_data <- bestem_data %>% 
  rowwise() %>%
  mutate(belongingness_cslc = mean(c_across(139:146)))

bestem_data$`17_fit major_1` <- as.numeric(bestem_data$`17_fit major_1`)
bestem_data$`17_welcome major_1` <- as.numeric(bestem_data$`17_welcome major_1`)
bestem_data$`17_comfort major_1` <- as.numeric(bestem_data$`17_comfort major_1`)
bestem_data$`17_thrilled major_1` <- as.numeric(bestem_data$`17_thrilled major_1`)
bestem_data$`17_like peers_1` <-  as.numeric(bestem_data$`17_like peers_1`)
bestem_data$`17_comfort peers_1` <- as.numeric(bestem_data$`17_comfort peers_1`)
bestem_data$`17_like profs_1` <-  as.numeric(bestem_data$`17_like profs_1`)
bestem_data$`17_comfort profs_1` <-  as.numeric(bestem_data$`17_comfort profs_1`)

bestem_data <- bestem_data %>% 
  rowwise() %>%
  mutate(belongingness_dwa = mean(c_across(148:155)))

bestem_data$`18_fit major_1` <- as.numeric(bestem_data$`18_fit major_1`)
bestem_data$`18_welcome major_1` <- as.numeric(bestem_data$`18_welcome major_1`)
bestem_data$`18_comfort major_1` <- as.numeric(bestem_data$`18_comfort major_1`)
bestem_data$`18_thrilled major_1` <- as.numeric(bestem_data$`18_thrilled major_1`)
bestem_data$`18_like peers_1` <-  as.numeric(bestem_data$`18_like peers_1`)
bestem_data$`18_comfort peers_1` <- as.numeric(bestem_data$`18_comfort peers_1`)
bestem_data$`18_like profs_1` <-  as.numeric(bestem_data$`18_like profs_1`)
bestem_data$`18_comfort profs_1` <-  as.numeric(bestem_data$`18_comfort profs_1`)

bestem_data <- bestem_data %>% 
  rowwise() %>%
  mutate(belongingness_east_asian_studies = mean(c_across(157:164)))

bestem_data$`19_fit major_1` <- as.numeric(bestem_data$`19_fit major_1`)
bestem_data$`19_welcome major_1` <- as.numeric(bestem_data$`19_welcome major_1`)
bestem_data$`19_comfort major_1` <- as.numeric(bestem_data$`19_comfort major_1`)
bestem_data$`19_thrilled major_1` <- as.numeric(bestem_data$`19_thrilled major_1`)
bestem_data$`19_like peers_1` <-  as.numeric(bestem_data$`19_like peers_1`)
bestem_data$`19_comfort peers_1` <- as.numeric(bestem_data$`19_comfort peers_1`)
bestem_data$`19_like profs_1` <-  as.numeric(bestem_data$`19_like profs_1`)
bestem_data$`19_comfort profs_1` <-  as.numeric(bestem_data$`19_comfort profs_1`)

bestem_data <- bestem_data %>% 
  rowwise() %>%
  mutate(belongingness_econ = mean(c_across(166:173)))

bestem_data$`20_fit major_1` <- as.numeric(bestem_data$`20_fit major_1`)
bestem_data$`20_welcome major_1` <- as.numeric(bestem_data$`20_welcome major_1`)
bestem_data$`20_comfort major_1` <- as.numeric(bestem_data$`20_comfort major_1`)
bestem_data$`20_thrilled major_1` <- as.numeric(bestem_data$`20_thrilled major_1`)
bestem_data$`20_like peers_1` <-  as.numeric(bestem_data$`20_like peers_1`)
bestem_data$`20_comfort peers_1` <- as.numeric(bestem_data$`20_comfort peers_1`)
bestem_data$`20_like profs_1` <-  as.numeric(bestem_data$`20_like profs_1`)
bestem_data$`20_comfort profs_1` <-  as.numeric(bestem_data$`20_comfort profs_1`)

bestem_data <- bestem_data %>% 
  rowwise() %>%
  mutate(belongingness_english = mean(c_across(175:182)))

bestem_data$`21_fit major_1` <- as.numeric(bestem_data$`21_fit major_1`)
bestem_data$`21_welcome major_1` <- as.numeric(bestem_data$`21_welcome major_1`)
bestem_data$`21_comfort major_1` <- as.numeric(bestem_data$`21_comfort major_1`)
bestem_data$`21_thrilled major_1` <- as.numeric(bestem_data$`21_thrilled major_1`)
bestem_data$`21_like peers_1` <-  as.numeric(bestem_data$`21_like peers_1`)
bestem_data$`21_comfort peers_1` <- as.numeric(bestem_data$`21_comfort peers_1`)
bestem_data$`21_like profs_1` <-  as.numeric(bestem_data$`21_like profs_1`)
bestem_data$`21_comfort profs_1` <-  as.numeric(bestem_data$`21_comfort profs_1`)

bestem_data <- bestem_data %>% 
  rowwise() %>%
  mutate(belongingness_french = mean(c_across(184:191)))

bestem_data$`22_fit major_1` <- as.numeric(bestem_data$`22_fit major_1`)
bestem_data$`22_welcome major_1` <- as.numeric(bestem_data$`22_welcome major_1`)
bestem_data$`22_comfort major_1` <- as.numeric(bestem_data$`22_comfort major_1`)
bestem_data$`22_thrilled major_1` <- as.numeric(bestem_data$`22_thrilled major_1`)
bestem_data$`22_like peers_1` <-  as.numeric(bestem_data$`22_like peers_1`)
bestem_data$`22_comfort peers_1` <- as.numeric(bestem_data$`22_comfort peers_1`)
bestem_data$`22_like profs_1` <-  as.numeric(bestem_data$`22_like profs_1`)
bestem_data$`22_comfort profs_1` <-  as.numeric(bestem_data$`22_comfort profs_1`)

bestem_data <- bestem_data %>% 
  rowwise() %>%
  mutate(belongingness_group_lang = mean(c_across(193:200)))

bestem_data$`23_fit major_1` <- as.numeric(bestem_data$`23_fit major_1`)
bestem_data$`23_welcome major_1` <- as.numeric(bestem_data$`23_welcome major_1`)
bestem_data$`23_comfort major_1` <- as.numeric(bestem_data$`23_comfort major_1`)
bestem_data$`23_thrilled major_1` <- as.numeric(bestem_data$`23_thrilled major_1`)
bestem_data$`23_like peers_1` <-  as.numeric(bestem_data$`23_like peers_1`)
bestem_data$`23_comfort peers_1` <- as.numeric(bestem_data$`23_comfort peers_1`)
bestem_data$`23_like profs_1` <-  as.numeric(bestem_data$`23_like profs_1`)
bestem_data$`23_comfort profs_1` <-  as.numeric(bestem_data$`23_comfort profs_1`)

bestem_data <- bestem_data %>% 
  rowwise() %>%
  mutate(belongingness_history = mean(c_across(202:209)))

bestem_data$`24_fit major_1` <- as.numeric(bestem_data$`24_fit major_1`)
bestem_data$`24_welcome major_1` <- as.numeric(bestem_data$`24_welcome major_1`)
bestem_data$`24_comfort major_1` <- as.numeric(bestem_data$`24_comfort major_1`)
bestem_data$`24_thrilled major_1` <- as.numeric(bestem_data$`24_thrilled major_1`)
bestem_data$`24_like peers_1` <-  as.numeric(bestem_data$`24_like peers_1`)
bestem_data$`24_comfort peers_1` <- as.numeric(bestem_data$`24_comfort peers_1`)
bestem_data$`24_like profs_1` <-  as.numeric(bestem_data$`24_like profs_1`)
bestem_data$`24_comfort profs_1` <-  as.numeric(bestem_data$`24_comfort profs_1`)

bestem_data <- bestem_data %>% 
  rowwise() %>%
  mutate(belongingness_japanese_studies = mean(c_across(211:218)))

bestem_data$`25_fit major_1` <- as.numeric(bestem_data$`25_fit major_1`)
bestem_data$`25_welcome major_1` <- as.numeric(bestem_data$`25_welcome major_1`)
bestem_data$`25_comfort major_1` <- as.numeric(bestem_data$`25_comfort major_1`)
bestem_data$`25_thrilled major_1` <- as.numeric(bestem_data$`25_thrilled major_1`)
bestem_data$`25_like peers_1` <-  as.numeric(bestem_data$`25_like peers_1`)
bestem_data$`25_comfort peers_1` <- as.numeric(bestem_data$`25_comfort peers_1`)
bestem_data$`25_like profs_1` <-  as.numeric(bestem_data$`25_like profs_1`)
bestem_data$`25_comfort profs_1` <-  as.numeric(bestem_data$`25_comfort profs_1`)

bestem_data <- bestem_data %>% 
  rowwise() %>%
  mutate(belongingness_latinx_studies = mean(c_across(220:227)))

bestem_data$`26_fit major_1` <- as.numeric(bestem_data$`26_fit major_1`)
bestem_data$`26_welcome major_1` <- as.numeric(bestem_data$`26_welcome major_1`)
bestem_data$`26_comfort major_1` <- as.numeric(bestem_data$`26_comfort major_1`)
bestem_data$`26_thrilled major_1` <- as.numeric(bestem_data$`26_thrilled major_1`)
bestem_data$`26_like peers_1` <-  as.numeric(bestem_data$`26_like peers_1`)
bestem_data$`26_comfort peers_1` <- as.numeric(bestem_data$`26_comfort peers_1`)
bestem_data$`26_like profs_1` <-  as.numeric(bestem_data$`26_like profs_1`)
bestem_data$`26_comfort profs_1` <-  as.numeric(bestem_data$`26_comfort profs_1`)

bestem_data <- bestem_data %>% 
  rowwise() %>%
  mutate(belongingness_mac = mean(c_across(229:236)))

bestem_data$`27_fit major_1` <- as.numeric(bestem_data$`27_fit major_1`)
bestem_data$`27_welcome major_1` <- as.numeric(bestem_data$`27_welcome major_1`)
bestem_data$`27_comfort major_1` <- as.numeric(bestem_data$`27_comfort major_1`)
bestem_data$`27_thrilled major_1` <- as.numeric(bestem_data$`27_thrilled major_1`)
bestem_data$`27_like peers_1` <-  as.numeric(bestem_data$`27_like peers_1`)
bestem_data$`27_comfort peers_1` <- as.numeric(bestem_data$`27_comfort peers_1`)
bestem_data$`27_like profs_1` <-  as.numeric(bestem_data$`27_like profs_1`)
bestem_data$`27_comfort profs_1` <-  as.numeric(bestem_data$`27_comfort profs_1`)

bestem_data <- bestem_data %>% 
  rowwise() %>%
  mutate(belongingness_music = mean(c_across(238:245)))

bestem_data$`28_fit major_1` <- as.numeric(bestem_data$`28_fit major_1`)
bestem_data$`28_welcome major_1` <- as.numeric(bestem_data$`28_welcome major_1`)
bestem_data$`28_comfort major_1` <- as.numeric(bestem_data$`28_comfort major_1`)
bestem_data$`28_thrilled major_1` <- as.numeric(bestem_data$`28_thrilled major_1`)
bestem_data$`28_like peers_1` <-  as.numeric(bestem_data$`28_like peers_1`)
bestem_data$`28_comfort peers_1` <- as.numeric(bestem_data$`28_comfort peers_1`)
bestem_data$`28_like profs_1` <-  as.numeric(bestem_data$`28_like profs_1`)
bestem_data$`28_comfort profs_1` <-  as.numeric(bestem_data$`28_comfort profs_1`)

bestem_data <- bestem_data %>% 
  rowwise() %>%
  mutate(belongingness_philosophy = mean(c_across(247:254)))

bestem_data$`29_fit major_1` <- as.numeric(bestem_data$`29_fit major_1`)
bestem_data$`29_welcome major_1` <- as.numeric(bestem_data$`29_welcome major_1`)
bestem_data$`29_comfort major_1` <- as.numeric(bestem_data$`29_comfort major_1`)
bestem_data$`29_thrilled major_1` <- as.numeric(bestem_data$`29_thrilled major_1`)
bestem_data$`29_like peers_1` <-  as.numeric(bestem_data$`29_like peers_1`)
bestem_data$`29_comfort peers_1` <- as.numeric(bestem_data$`29_comfort peers_1`)
bestem_data$`29_like profs_1` <-  as.numeric(bestem_data$`29_like profs_1`)
bestem_data$`29_comfort profs_1` <-  as.numeric(bestem_data$`29_comfort profs_1`)

bestem_data <- bestem_data %>% 
  rowwise() %>%
  mutate(belongingness_politics = mean(c_across(256:263)))

bestem_data$`30_fit major_1` <- as.numeric(bestem_data$`30_fit major_1`)
bestem_data$`30_welcome major_1` <- as.numeric(bestem_data$`30_welcome major_1`)
bestem_data$`30_comfort major_1` <- as.numeric(bestem_data$`30_comfort major_1`)
bestem_data$`30_thrilled major_1` <- as.numeric(bestem_data$`30_thrilled major_1`)
bestem_data$`30_like peers_1` <-  as.numeric(bestem_data$`30_like peers_1`)
bestem_data$`30_comfort peers_1` <- as.numeric(bestem_data$`30_comfort peers_1`)
bestem_data$`30_like profs_1` <-  as.numeric(bestem_data$`30_like profs_1`)
bestem_data$`30_comfort profs_1` <-  as.numeric(bestem_data$`30_comfort profs_1`)

bestem_data <- bestem_data %>% 
  rowwise() %>%
  mutate(belongingness_rels = mean(c_across(265:272)))

bestem_data$`31_fit major_1` <- as.numeric(bestem_data$`31_fit major_1`)
bestem_data$`31_welcome major_1` <- as.numeric(bestem_data$`31_welcome major_1`)
bestem_data$`31_comfort major_1` <- as.numeric(bestem_data$`31_comfort major_1`)
bestem_data$`31_thrilled major_1` <- as.numeric(bestem_data$`31_thrilled major_1`)
bestem_data$`31_like peers_1` <-  as.numeric(bestem_data$`31_like peers_1`)
bestem_data$`31_comfort peers_1` <- as.numeric(bestem_data$`31_comfort peers_1`)
bestem_data$`31_like profs_1` <-  as.numeric(bestem_data$`31_like profs_1`)
bestem_data$`31_comfort profs_1` <-  as.numeric(bestem_data$`31_comfort profs_1`)

bestem_data <- bestem_data %>% 
  rowwise() %>%
  mutate(belongingness_soc = mean(c_across(274:281)))

bestem_data$`32_fit major_1` <- as.numeric(bestem_data$`32_fit major_1`)
bestem_data$`32_welcome major_1` <- as.numeric(bestem_data$`32_welcome major_1`)
bestem_data$`32_comfort major_1` <- as.numeric(bestem_data$`32_comfort major_1`)
bestem_data$`32_thrilled major_1` <- as.numeric(bestem_data$`32_thrilled major_1`)
bestem_data$`32_like peers_1` <-  as.numeric(bestem_data$`32_like peers_1`)
bestem_data$`32_comfort peers_1` <- as.numeric(bestem_data$`32_comfort peers_1`)
bestem_data$`32_like profs_1` <-  as.numeric(bestem_data$`32_like profs_1`)
bestem_data$`32_comfort profs_1` <-  as.numeric(bestem_data$`32_comfort profs_1`)

bestem_data <- bestem_data %>% 
  rowwise() %>%
  mutate(belongingness_spanish = mean(c_across(283:290)))

bestem_data$`33_fit major_1` <- as.numeric(bestem_data$`33_fit major_1`)
bestem_data$`33_welcome major_1` <- as.numeric(bestem_data$`33_welcome major_1`)
bestem_data$`33_comfort major_1` <- as.numeric(bestem_data$`33_comfort major_1`)
bestem_data$`33_thrilled major_1` <- as.numeric(bestem_data$`33_thrilled major_1`)
bestem_data$`33_like peers_1` <-  as.numeric(bestem_data$`33_like peers_1`)
bestem_data$`33_comfort peers_1` <- as.numeric(bestem_data$`33_comfort peers_1`)
bestem_data$`33_like profs_1` <-  as.numeric(bestem_data$`33_like profs_1`)
bestem_data$`33_comfort profs_1` <-  as.numeric(bestem_data$`33_comfort profs_1`)

bestem_data <- bestem_data %>% 
  rowwise() %>%
  mutate(belongingness_theater = mean(c_across(292:299)))

bestem_data$`34_fit major_1` <- as.numeric(bestem_data$`34_fit major_1`)
bestem_data$`34_welcome major_1` <- as.numeric(bestem_data$`34_welcome major_1`)
bestem_data$`34_comfort major_1` <- as.numeric(bestem_data$`34_comfort major_1`)
bestem_data$`34_thrilled major_1` <- as.numeric(bestem_data$`34_thrilled major_1`)
bestem_data$`34_like peers_1` <-  as.numeric(bestem_data$`34_like peers_1`)
bestem_data$`34_comfort peers_1` <- as.numeric(bestem_data$`34_comfort peers_1`)
bestem_data$`34_like profs_1` <-  as.numeric(bestem_data$`34_like profs_1`)
bestem_data$`34_comfort profs_1` <-  as.numeric(bestem_data$`34_comfort profs_1`)

bestem_data <- bestem_data %>% 
  rowwise() %>%
  mutate(belongingness_uep = mean(c_across(301:308)))

# No data on independent study majors

```

"Belongingness in STEM" metric (Average the responses to all questions by each major)
```{r}
belongingness_averages <- bestem_data %>%
  distinct(across(contains("belongingness")))

colMeans(belongingness_averages, na.rm = T)
```

Research Experience Metric (0 = none, 1 = any exp., 1 exp., 2 = two experiences, 3 = 3+ experiences picked) 
```{r}
bestem_data %>% 
  distinct(`research experiences`)
  
bestem_data <- bestem_data %>% 
  mutate(research_experiences = case_when(
    `research experiences` == "Academic year research (e.g., directed or mentored research)" ~ "1",
    `research experiences` == "STEM-related internship" ~ "1",
    `research experiences` == "Summer research experience outside of Oxy" ~ "1",
    `research experiences` == "Summer research experience at Oxy" ~ "1",
    `research experiences` == "Summer research experience outside of Oxy,STEM-related internship" ~ "2",
    `research experiences` == "Academic year research (e.g., directed or mentored research),STEM-related internship" ~ "2",
    `research experiences` == "Academic year research (e.g., directed or mentored research),Summer research experience at Oxy" ~ "2",
    `research experiences` == "Summer research experience at Oxy,STEM-related internship" ~ "2",
    `research experiences` == "Academic year research (e.g., directed or mentored research),Summer research experience outside of Oxy" ~ "2",
    `research experiences` == "Academic year research (e.g., directed or mentored research),Summer research experience outside of Oxy,STEM-related internship" ~ "3",
    `research experiences` == "Academic year research (e.g., directed or mentored research),Summer research experience at Oxy,Summer research experience outside of Oxy" ~ "3",
    `research experiences` == "Academic year research (e.g., directed or mentored research),Summer research experience at Oxy,Summer research experience outside of Oxy,STEM-related internship" ~ "3",
    `research experiences` == "Academic year research (e.g., directed or mentored research),Summer research experience at Oxy,STEM-related internship" ~ "3",
    TRUE ~ "0"))
```

Visiting peer advisor/ TA office hours (NA = didn't answer it, 0 = Never, 1 = Less than once a semester, 2 = Once or twice a semester, 3 = A few times a semester, 4 = weekly or more often) 

```{r}
bestem_data %>% 
  distinct(`office hours`)

bestem_data <- bestem_data %>% 
  mutate(office_hours = case_when(
    `office hours` == "Never" ~ "0",
    `office hours` == "A few times a semester" ~ "3",
    `office hours` == "Once or twice in a semester" ~ "2",
    `office hours` == "Less than once a semester" ~ "1",
    `office hours` == "Weekly or more often" ~ "4",
    TRUE ~ "0"))
```

Study Groups (0 = No, 1 = Yes)
```{r}
bestem_data %>% 
  distinct(`study groups`)

bestem_data <- bestem_data %>% 
  mutate(study_groups = case_when(
    `study groups` == "No" ~ "0",
    `study groups`== "Yes" ~ "1",
    TRUE ~ "0"))
```


AMP (0 = NA's, no participation, 1 = visited peer office hours rarely or very occasionally, 2 = students indicated taking full advantage of peer office hours)
```{r}
bestem_data %>% 
  distinct(AMP)

bestem_data <- bestem_data %>% 
  mutate(utilize_AMP = case_when(
    `AMP` == "Other" ~ "0",
    `AMP` == "Didn't attend as it did not apply to any of my courses" ~ "0",
    `AMP` == "Didn't attend as it did not apply to any of my courses,Other" ~ "0",
    `AMP` == "Attended sometimes for one or more courses" ~ "1",
    `AMP` == "Didn't attend as it did not apply to any of my courses,Attended sometimes for one or more courses"
    ~ "1",
    `AMP` == "Attended frequently for one or more courses" ~ "2",
    `AMP` == "Attended frequently for one or more courses,Served as a facilitator" ~ "2",
    `AMP` == "Attended sometimes for one or more courses,Attended frequently for one or more courses" 
    ~ "2",
    `AMP` == "Served as a facilitator" ~ "2",
    `AMP` == "Attended sometimes for one or more courses,Served as a facilitator" ~ "2",
    TRUE ~ "0"))

```

SSAP (0 = NA's, no participation, 1 = visited peer office hours rarely or very occasionally, 2 = students indicated taking full advantage of peer office hours)
```{r}
bestem_data %>% 
  distinct(SSAP)

bestem_data <- bestem_data %>% 
  mutate(utilize_SSAP = case_when(
    `SSAP` == "Other" ~ "0",
    `SSAP` == "Didn't attend as it did not apply to any of my courses" ~ "0",
    `SSAP` == "Attended sometimes for one or more courses" ~ "1",
    `SSAP` == "Attended sometimes for one or more courses,Other" ~ "1",
    `SSAP` == "Didn't attend as it did not apply to any of my courses,Attended sometimes for one or more courses"
    ~ "1",
    `SSAP` == "Attended frequently for one or more courses" ~ "2",
    `SSAP` == "Attended frequently for one or more courses,Served as a facilitator" ~ "2",
    `SSAP` == "Attended sometimes for one or more courses,Attended frequently for one or more courses" 
    ~ "2",
    `SSAP` == "Served as a facilitator" ~ "2",
    `SSAP` == "Attended sometimes for one or more courses,Served as a facilitator" ~ "2",
    TRUE ~ "0"))

```

"Peer Learning" Score (New variable called peer learning (study groups, AMP, SSAP, and peer OH))
```{r}
bestem_data$study_groups <- as.numeric(bestem_data$study_groups)
bestem_data$utilize_AMP <- as.numeric(bestem_data$utilize_AMP)
bestem_data$utilize_SSAP <- as.numeric(bestem_data$utilize_SSAP)
bestem_data$office_hours <- as.numeric(bestem_data$office_hours)

bestem_data <- bestem_data %>%
  rowwise() %>%
  mutate(peer_learning_score = mean(c_across(383:386)))
```

```{r}
bestem_data %>%
  distinct(clubs_1_TEXT)

bestem_data <- bestem_data %>%
  mutate(club = case_when(
    `clubs_1_TEXT` == "" ~ "1",
    `clubs_1_TEXT` == "" ~ "1",
    TRUE ~ "0"))

```

STEM-related clubs (0 = no clubs, 1 = one club, 2 = multiple clubs)
```{r}

```

Export  
```{r}
# write_csv(bestem_data, "bestem_data_07012021.csv")
```
