---
title: "Belonging in STEM survey tidysesh"
author: "JP Flores"
date: "5/3/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load the packages 
```{r}
library(tidyverse)
library(readxl)
library(janitor)
library(plotly)
```

Import the data
```{r}
bestem_data <-read_csv("/Users/jpflores/Desktop/Desktop - JP’s MacBook Pro/bestem/data through 5_30.xlsx - anonymizing the data.csv")

# View(bestem_data)

bestem_data <- bestem_data %>% 
  select(- `Row # from Qualtrics`,
         - ResponseId,- X15, - X16, - X17, - X27, - X28, - X29, - X39, - X40,
         - X41, - X51, - X52, - X53, - X63, - X64, - X65, - X75, - X76, - X77, - X87, - X88, - X89,
         - X99, - X100, - X101, - X111, - X112, - X113, - X123, - X124, - X125, - X135, - X136,
         - X137, - X147, - X148, - X149, - X159, - X160, - X161, - X171, - X172, - X173, - X183,
         - X184, - X185, - X195, - X196, - X197, - X207, - X208, - X209, - X219, - X220,
         - X221, - X231, - X232, - X233, - X243, - X244, - X245, - X255, - X256, - X257,- X267,
         - X268, - X269, - X279, - X280, - X281, - X291, - X292, - X293, - X303, -X304, - X305,
         - X315, - X316, - X317, - X327, - X328, - X329, - X339, - X340, - X341, - X351, - X352,
         - X353, - X363, - X364, - X365, - X375, - X376, - X377, - X387, - X388, - X389, - X399,
         - X400, - X401, - X411, - X412, - X413, - X423, - X424, - X438, - X440, - X441, - X442, - X443, 
         - X444, - X445, - X447, - X448
         )

bestem_data <- bestem_data[-c(1:2) , ]

bestem_data %>%
  count(major)

```

Export for Sherman and Levitan for further direction on how to organize the data 
```{r}
write_csv(bestem_data, "bestem_data_06222021.csv")
```


Add column (Were they a declared STEM major? ex. Biochemistry, Biology, Chemistry, Computer Science, Cognitive Science, Geology, Kinesiology, Mathematics, Physics, or Psychology)
```{r}
declared_stem <- bestem_data %>% 
  filter(any_STEM == "Yes") %>% 
  filter(know_major == "Yes") %>% 
  filter(major %in% c("Biology", "Biochemistry", "Chemistry", "Computer Science", "Cognitive   Science","Geology","Kinesiology", "Mathematics", "Physics", "Psychology", "Computer Science,Economics", "Cognitive Science,Philosophy", "Cognitive Science,Group Language", "Biology,Kinesiology,Psychology", "Computer Science,Economics", "Art & Art History,Biology",
"Biochemistry,Biology", "Biochemistry,Computer Science", "Biochemistry,Theater",
"Biology,Theater", "Biology,Cognitive Science", "Chemistry,Chinese Studies", "Cognitive Science,Computer Science", "Cognitive Science,Economics", "Cognitive Science,Theater", "Comparative Studies in Literature and Culture,Computer Science", "Comparative Studies in Literature and Culture,Mathematics", "Computer Science,Mathematics", "Computer Science,Media Arts & Culture",
"Computer Science,Physics", "Computer Science,Theater", "Economics,Mathematics", "Mathematics,Physics", "Psychology,Spanish Studies"))

         
bestem_data <- bestem_data %>%
  mutate(stem_major = case_when(
    major == "Biology" ~ "yes", 
    major == "Biochemistry" ~ "yes",
    major == "Chemistry" ~ "yes",
    major == "Computer Science" ~ "yes",
    major == "Cognitive Science" ~ "yes",
    major == "Geology" ~ "yes",
    major == "Kinesiology" ~ "yes",
    major == "Mathematics" ~ "yes",
    major == "Physics" ~ "yes",
    major == "Psychology" ~ "yes",
    major == "Art & Art History,Biology" ~ "yes",
    major == "Biochemistry,Biology" ~ "yes",
    major == "Biochemistry,Comparative Studies in Literature and Culture" ~ "yes",
    major == "Biochemistry,Computer Science" ~ "yes",
    major == "Biochemistry,Theater" ~ "yes",
    major == "Biology,Kinesiology,Psychology" ~ "yes",
    major == "Biology,Theater" ~ "yes",
    major == "Biology,Cognitive Science" ~ "yes",
    major == "Computer Science,Economics" ~ "yes",
    major == "Cognitive Science,Philosophy" ~ "yes",
    major == "Cognitive Science,Group Language" ~ "yes",
    major == "Chemistry,Chinese Studies" ~ "yes",
    major == "Cognitive Science,Computer Science" ~ "yes",
    major == "Cognitive Science,Economics" ~ "yes",
    major == "Cognitive Science,Theater" ~ "yes",
    major == "Comparative Studies in Literature and Culture,Computer Science" ~ "yes",
    major == "Comparative Studies in Literature and Culture,Mathematics" ~ "yes",
    major == "Computer Science,Mathematics" ~ "yes",
    major == "Computer Science,Media Arts & Culture" ~ "yes",
    major == "Computer Science,Physics" ~ "yes",
    major == "Computer Science,Theater" ~ "yes",
    major == "Economics,Mathematics" ~ "yes",
    major == "Mathematics,Physics" ~ "yes",
    major == "Psychology,Spanish Studies" ~ "yes",
    TRUE ~ "no"))
    # TRUE ~ NA_character_))
```

Add column (Were they an intended STEM major?)
```{r}
bestem_data <- bestem_data %>%
  mutate(intention_in_stem = case_when(
  know_major == "Not sure of the exact major, but something in STEM" ~ "yes",
  know_major == "Not sure of the major, definitely not STEM" ~ "none",
  know_major == "Not sure of the major, might be in STEM" ~ "undecided",
  know_major == "Yes" ~ "declared",
  know_major == "No, but I've already figured out my intended major(s)" ~ "figured it out",
  TRUE ~ NA_character_))
```

<!-- Add column (Undecided majors) -->
<!-- ```{r} -->

<!-- ``` -->

<!-- Add column (Non-STEM majors) -->
<!-- ```{r} -->
<!-- ``` -->

Add column (double STEM major)
```{r}
bestem_data <- bestem_data %>% 
  mutate(double_stem = case_when(
    major == "Biochemistry,Biology" ~ "yes",
    major == "Biochemistry,Computer Science" ~ "yes",
    major == "Biology,Kinesiology,Psychology" ~ "yes",
    major == "Biology,Cognitive Science" ~ "yes",
    major == "Cognitive Science,Computer Science" ~ "yes",
    major == "Computer Science,Mathematics" ~ "yes",
    major == "Computer Science,Physics" ~ "yes",
    major == "Mathematics,Physics" ~ "yes",
    TRUE ~ "no"))
```

Add column (double non-STEM major)
```{r}
bestem_data <- bestem_data %>% 
  mutate(double_non_stem = case_when(
    major == "Art & Art History,Biology" ~ "yes",
    major == "Biochemistry,Comparative Studies in Literature and Culture" ~ "yes",
    major == "Biochemistry,Theater" ~ "yes",
    major == "Biology,Theater" ~ "yes",
    major == "Computer Science,Economics" ~ "yes",
    major == "Cognitive Science,Philosophy" ~ "yes",
    major == "Cognitive Science,Group Language" ~ "yes",
    major == "Chemistry,Chinese Studies" ~ "yes",
    major == "Cognitive Science,Economics" ~ "yes",
    major == "Cognitive Science,Theater" ~ "yes",
    major == "Comparative Studies in Literature and Culture,Computer Science" ~ "yes",
    major == "Comparative Studies in Literature and Culture,Mathematics" ~ "yes",
    major == "Computer Science,Media Arts & Culture" ~ "yes",
    major == "Computer Science,Theater" ~ "yes",
    major == "Economics,Mathematics" ~ "yes",
    major == "Psychology,Spanish Studies" ~ "yes",
    TRUE ~ "no"))
```

<!-- Add column (double major: STEM and non-STEM) -->
<!-- ```{r} -->

<!-- ``` -->

<!-- Maybe add column (STEM-affiliated or nah?) -->
<!-- ```{r} -->

<!-- ``` -->

"Belongingness in STEM" metric (Average the responses to all questions by individual by first major)
```{r}

```

"Belongingness in STEM" metric (Average the responses to all questions by individual by second major)
```{r}

```

"Belongingness in STEM" metric (Average the responses to all questions by individual by third major)
```{r}

```

"Belongingness in STEM" metric (Average the responses to all questions by each major)
```{r}

```

Research Experience Metric (0 = none, 1 = any exp., 1 exp., 2 = two experiences, 3 = 3+ experiences picked) + "Belongingness" Score
```{r}

```


Peer Learning/ Support (Peer OH's, ) (0 = NA's, no participation, 1 = visited peer office hours rarely or very occasionally, 2 = students indicated taking full advantage of peer office hours)
```{r}

```

AMP/SSAP (0 = NA's, no participation, 1 = visited peer office hours rarely or very occasionally, 2 = students indicated taking full advantage of peer office hours)
```{r}

```

STEM-related clubs (0 = students indicated no participation, 1 = students indicated that they were a member of a STEM-related club, 2 = students indicated that they held a leadership position)
```{r}

```

Visiting peer advisor/ TA office hours (NA = didn't answer it, 0 = never went, 1 = Never,2 = Less than once a semseter, 3 = Once or twice a semester, 4 = ) + separate than a "Belongingness" Score (New variable called peer learning (study groups, AMP, SSAP, and peer OH))
```{r}

```

STEM-related clubs (0 = no clubs, 1 = one club, 2 = multiple clubs)
```{r}

```

